---
title: "Flow Cytometry Analysis"
author: "`r paste0('  ','Author', ': ',Sys.getenv('USERNAME'))`"
date: "`r paste0('  ','Date', ': ', format(Sys.time(), '%d %B %Y'))`"
output:
  html_notebook:
    toc: true
    toc_float: true
    toc_depth: 3
    css: ./HTML_source/style.css
---

This protocl was modified from [HERE](https://jchellmuth.com/posts/FACS-with-R/).

## 00.Setting R Enviroment {.tabset .tabset-fade}

### 1.Installation & Loading Packages

```{r}
if (!require(cytolib)) remotes::install_github("RGLab/cytolib")
list.of.packages <- c("tidyverse","BH","data.table")
list.of.packages.Bio <- c("flowCore","ggcyto","flowStats","flowWorkspace","openCyto")
#Packages that does not install yet
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[, "Package"])]
new.packages.Bio <- list.of.packages.Bio[!(list.of.packages.Bio %in% installed.packages()[, "Package"])]
#install required packages
if(length(new.packages)) {install.packages(new.packages)}
if (!requireNamespace("BiocManager", quietly = TRUE)){install.packages("BiocManager")}
if(length(new.packages.Bio)) {BiocManager::install(new.packages.Bio)}
#How to install the C++ Boost Libraries on Windows
#https://andres.jaimes.net/718/how-to-install-the-c-boost-libraries-on-windows/
#if (!require(velocyto)) devtools::install_github("velocyto-team/velocyto.R")
#Loading all packages
invisible(lapply(c(list.of.packages,list.of.packages.Bio), library, character.only = TRUE))
rm(list.of.packages,list.of.packages.Bio,new.packages,new.packages.Bio)
```

### 2.Loading FCS files and label

```{r}
# Please set up "pattern" and "subset.CoNa"
pattern<-c("^CRL.*\\.fcs$", "^Negative_.*\\.fcs$")
subset.CoNa<-list(
  c("Time","HDR.CE","HDR.SE","HDR.V","FSC.A","SSC.A","FL4.A","FL7.A"),
  c("HDR.T","HDR.CE","HDR.SE","HDR.V","FSC.A","SSC.A","B2.A","R1.A")
)

for(i in 1:length(pattern)){
  if(i==1){
    fs <- read.flowSet(
      path = ".",
      pattern = pattern[i],
      alter.names = T,
      emptyValue=FALSE,
      truncate_max_range = FALSE,
      column.pattern="[^W]$")
    fs <- fs[,subset.CoNa[[i]]]
  }else{
    temp <- read.flowSet(
      path = ".",
      pattern = pattern[i],
      alter.names = T,
      transformation="scale",
      decades=1,
      emptyValue=FALSE,
      truncate_max_range = FALSE,
      column.pattern="[^W]$")
    temp <- temp[,subset.CoNa[[i]]]
    colnames(temp)<-colnames(fs)
    markernames(temp)<-markernames(fs)
    temp2 <- read.flowSet(
      path = ".",
      pattern = pattern[i],
      alter.names = T,
      emptyValue=FALSE,
      truncate_max_range = FALSE,
      column.pattern="[^W]$")
    temp2 <- temp2[,subset.CoNa[[i]]]
    colnames(temp2)<-colnames(fs)
    markernames(temp2)<-markernames(fs)
    for (j in 1:length(temp2)) {
      temp[[j]]@exprs[,2:6]<-temp2[[j]]@exprs[,2:6]
    }
    fs<-rbind2(fs,temp)
  }
}

for (i in 1:length(fs)) {
  for(k in 1:length(subset.CoNa[[1]])){
    fs[[i]]@exprs[,k][fs[[i]]@exprs[,k]==-Inf]<-min(fs[[i]]@exprs[,k][fs[[i]]@exprs[,k]>-Inf],na.rm = TRUE)
    fs[[i]]@exprs[,k][fs[[i]]@exprs[,k]==Inf]<-max(fs[[i]]@exprs[,k][fs[[i]]@exprs[,k]<Inf],na.rm = TRUE)
  }
}

pData(fs)
pData(fs)$well <- lapply(str_split(sampleNames(fs), "[_.]"),"[[",2)%>%unlist() # extract well from name and add new 'well' column
pData(fs)

summary(fs)
```

### 3.Basic Information

```{r}
lapply(colnames(fs),getChannelMarker, frm=flowSet_to_list(fs)[[1]])%>%
  rbindlist()%>%as.data.frame()
```

### 3.Grouping and Naming

```{r}
pData(fs)$well<-factor(
  c(
    "Unlabeled Hb", "Hb-FL", "Hb-FL +Hp: 0.0001uM", "Hb-FL +Hp: 0.001uM", "Hb-FL +Hp: 0.01uM", "Hb-FL +Hp: 0.1uM", "Hb-FL +Hp: 1uM", "Hb-FL +Hp: 10uM",
  "Hb -FL", "Hb -FL +Hp: 1uM", "Hb -FL +Hp: 1uM +HMGB1: 0.1ug/ml", "Hb -FL +Hp: 1uM +HMGB1: 0.5ug/ml", "Hb -FL +Hp: 1uM +HMGB1: 1ug/ml", "Hb -FL +Hp: 1uM +HMGB1: 2ug/ml", "Hb -FL +Hp: 1uM +HMGB1: 5ug/ml", "Hb -FL +Hp: 1uM +HMGB1: 10ug/ml",
   "Unlabeled HMGB1", "HMGB1-FL", "HMGB1-FL +Hp: 1uM", "HMGB1-FL +Hp: 5uM", "HMGB1-FL +Hp: 10uM", "PBS", "Unlabled"
  ),
  levels = c(
    "Unlabeled Hb", "Hb-FL", "Hb-FL +Hp: 0.0001uM", "Hb-FL +Hp: 0.001uM", "Hb-FL +Hp: 0.01uM", "Hb-FL +Hp: 0.1uM", "Hb-FL +Hp: 1uM", "Hb-FL +Hp: 10uM",
    "Unlabeled HMGB1", "HMGB1-FL", "HMGB1-FL +Hp: 1uM", "HMGB1-FL +Hp: 5uM", "HMGB1-FL +Hp: 10uM",
    "Hb -FL", "Hb -FL +Hp: 1uM", "Hb -FL +Hp: 1uM +HMGB1: 0.1ug/ml", "Hb -FL +Hp: 1uM +HMGB1: 0.5ug/ml", "Hb -FL +Hp: 1uM +HMGB1: 1ug/ml", "Hb -FL +Hp: 1uM +HMGB1: 2ug/ml", "Hb -FL +Hp: 1uM +HMGB1: 5ug/ml", "Hb -FL +Hp: 1uM +HMGB1: 10ug/ml", "PBS", "Unlabled"
  )
)
pData(fs)$order<-sprintf("%03d", c(2:9,10:17,18:22,1,23))%>%as.character()
pData(fs)
```

## 01.Set Debris Gate {.tabset .tabset-fade}

### Processing

Convert data format

```{r}
colnames(fs)
gs <- GatingSet(fs)
pData(gs)$order<-pData(fs)$order
ID_mapping<-pData(gs)$well
names(ID_mapping)<-pData(gs)$orde
x_label<-"CD163"
y_label<-"Hb"
```

Get auto gate setting

```{r}
groups<-list(
  c(1:8),
  c(9:16),
  c(17:21),
  c(22:23)
)
groupNa<-c("G1","G2","G3","G4")
g.debris.ls<-list()
gp<-list()
target<-list(
  c(375,375),
  c(250,375),
  c(375,375),
  c(250,175)
)
quantile<-c(0.65,0.65,0.65,0.65)
for(i in 1:length(groups)){
  ff<-gh_pop_get_data(gs[[groups[[i]][1]]], y="root", returnType="flowFrame")
  for (k in groups[[i]][-1]) {
    temp<-gh_pop_get_data(gs[[k]], y="root", returnType="flowFrame")
    ff@exprs<-rbind(
      ff@exprs, temp@exprs
    )
  }
  chnl <- c("FSC.A", "SSC.A")
  
  g.debris <- openCyto:::.flowClust.2d(ff, channels = chnl, K=3,  target=target[[i]], quantile=0.85, filterId = "Debris")
  g.debris@filterId<-paste0("No Debris"," (",groupNa[i],")")
  rm(ff)
  
  g.debris.ls[[i]]<-g.debris
  
  for(k in 1:length(groups[[i]])){
    gp[[groups[[i]][k]]]<-ggcyto(gs[[groups[[i]][k]]], aes(x=FSC.A, y=SSC.A), subset="root")+
      geom_hex(bins = 1000)+
      geom_gate(g.debris.ls[[i]])+
      geom_stats(adjust = 0.8)+
      ggcyto_par_set(limits = "instrument")+
      theme_bw()+
      xlab("FSC-A") + ylab("SSC-A")
  }
  
}
```

Let's check the auto gate setting

```{r, fig.width=5, fig.height=4}
for(i in 1:length(gp)){
  gp[[i]]%>%plot()
}
```

Recompute if you confirmed the results above

```{r}
for(i in 1:length(groups)){
  gs_pop_add(gs, g.debris.ls[[i]], parent="root")
  recompute(gs)
}
```

## 02 Set Fluoresence Gate

### 02-01 Overview

```{r}
gp<-list()

for(i in 1:length(groups)){
  
  for(k in 1:length(groups[[i]])){
    gp[[groups[[i]][k]]]<-ggcyto(gs[[groups[[i]][k]]], aes(x=FL4.A,y=FL7.A), subset=paste0("No Debris"," (",groupNa[i],")"))+
      geom_hex(bins = 25)+
      scale_x_log10(
        breaks = scales::trans_breaks("log10", function(x) 10^x),
        labels = scales::trans_format("log10", scales::math_format(10^.x))
      ) +
      scale_y_log10(
        breaks = scales::trans_breaks("log10", function(x) 10^x),
        labels = scales::trans_format("log10", scales::math_format(10^.x))
      )+
      coord_cartesian(xlim = c(1e-2,1e3), ylim = c(1e-2,1e4))+
      theme_bw()+
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
      annotation_logticks()+
      xlab(x_label) + ylab(y_label)
      
  }
  
}
```


```{r fig.width=5, fig.height=4, results='hide', message=FALSE, warning=FALSE, fig.show='asis'}
for(i in 1:length(gp)){
  gp[[i]]%>%plot()
}
```

### 02-02 Processing {.tabset .tabset-fade}

#### Set Red Gate {.tabset .tabset-fade .tabset-dropdown}

##### 1.Gatting Value
Get the gating value from the density plot

```{r}
fr <- gh_pop_get_data(gs[[22]], y="No Debris (G4)", returnType = "flowFrame")
cut<-fr@exprs[,"FL7.A"]%>%quantile(.,1)
cut
```

##### 2.Gating Check

```{r fig.width=5, fig.height=4, results='hide', message=FALSE, warning=FALSE, fig.show='asis'}
g.red <- rectangleGate(filterId="Red Positive", "FL7.A"=c(cut, Inf)) # set gate

gp<-list()

for(i in 1:length(groups)){
  
  for(k in 1:length(groups[[i]])){
    gp[[groups[[i]][k]]]<-ggcyto(gs[[groups[[i]][k]]], aes(x=FL4.A,y=FL7.A), subset=paste0("No Debris"," (",groupNa[i],")"))+
      geom_hex(bins = 25)+
      geom_gate(g.red)+
      scale_x_log10(
        breaks = scales::trans_breaks("log10", function(x) 10^x),
        labels = scales::trans_format("log10", scales::math_format(10^.x))
      ) +
      scale_y_log10(
        breaks = scales::trans_breaks("log10", function(x) 10^x),
        labels = scales::trans_format("log10", scales::math_format(10^.x))
      )+
      coord_cartesian(xlim = c(1e-2,1e3), ylim = c(1e-2,1e4))+
      theme_bw()+
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
      annotation_logticks()+
      xlab(x_label) + ylab(y_label)
      
  }
  
}


for(i in 1:length(gp)){
  gp[[i]]%>%plot()
}

```

#### Set PI Gate {.tabset .tabset-fade .tabset-dropdown}

##### 1.Gatting Value
Get the gating value from the density plot

```{r}
fr <- gh_pop_get_data(gs[[22]], y="No Debris (G4)", returnType = "flowFrame")
cut<-fr@exprs[,"FL4.A"]%>%quantile(.,1)
cut
```

##### 3.Gatting Check

```{r fig.width=6, fig.height=4, results='hide', message=FALSE, warning=FALSE, fig.show='asis'}
g.PI <- rectangleGate(filterId="PI Positive", "FL4.A"=c(cut, Inf)) # set gate

gp<-list()

for(i in 1:length(groups)){
  
  for(k in 1:length(groups[[i]])){
    gp[[groups[[i]][k]]]<-ggcyto(gs[[groups[[i]][k]]], aes(x=FL4.A,y=FL7.A), subset=paste0("No Debris"," (",groupNa[i],")"))+
      geom_hex(bins = 25)+
      geom_gate(g.PI)+
      scale_x_log10(
        breaks = scales::trans_breaks("log10", function(x) 10^x),
        labels = scales::trans_format("log10", scales::math_format(10^.x))
      ) +
      scale_y_log10(
        breaks = scales::trans_breaks("log10", function(x) 10^x),
        labels = scales::trans_format("log10", scales::math_format(10^.x))
      )+
      coord_cartesian(xlim = c(1e-2,1e3), ylim = c(1e-2,1e4))+
      theme_bw()+
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
      annotation_logticks()+
      xlab(x_label) + ylab(y_label)
      
  }
  
}

for(i in 1:length(gp)){
  gp[[i]]%>%plot()
}
```

### 02-03 Red/PI Gate Combination {.tabset .tabset-fade}

#### Recompute

```{r}
PI.P_Red.P<-rectangleGate(filterId="PI+ Red+", "FL4.A"=c(g.PI@min, Inf), "FL7.A"=c(g.red@min, Inf))
PI.N_Red.N<-rectangleGate(filterId="PI- Red-", "FL4.A"=c(-Inf, g.PI@min), "FL7.A"=c(-Inf, g.red@min))
PI.P_Red.N<-rectangleGate(filterId="PI+ Red-", "FL4.A"=c(g.PI@min, Inf), "FL7.A"=c(-Inf, g.red@min))
PI.N_Red.P<-rectangleGate(filterId="PI- Red+", "FL4.A"=c(-Inf, g.PI@min), "FL7.A"=c(g.red@min, Inf))

for(i in 1:length(groups)){
  gs_pop_add(gs, PI.P_Red.P, parent=paste0("No Debris"," (",groupNa[i],")"))
  recompute(gs)
  gs_pop_add(gs, PI.N_Red.N, parent=paste0("No Debris"," (",groupNa[i],")"))
  recompute(gs)
  gs_pop_add(gs, PI.P_Red.N, parent=paste0("No Debris"," (",groupNa[i],")"))
  recompute(gs)
  gs_pop_add(gs, PI.N_Red.P, parent=paste0("No Debris"," (",groupNa[i],")"))
  recompute(gs)
}
```

#### Plot Out

```{r fig.width=6, fig.height=4, results='hide', message=FALSE, warning=FALSE, fig.show='asis', echo=FALSE}
gp<-list()

for(i in 1:length(groups)){
  
  for(k in 1:length(groups[[i]])){
    gp[[groups[[i]][k]]]<-ggcyto(gs[[groups[[i]][k]]], aes(x=FL4.A,y=FL7.A), subset=paste0("No Debris"," (",groupNa[i],")"))+
      geom_hex(bins = 25)+
      geom_gate(PI.P_Red.P)+
      geom_gate(PI.N_Red.N)+
      geom_gate(PI.P_Red.N)+
      geom_gate(PI.N_Red.P)+
      geom_stats(adjust = 0.2)+
      geom_hline(yintercept=g.red@min[["FL7.A"]], linetype="dotted", 
                color = "red", size=1)+
      geom_vline(xintercept = g.PI@min[["FL4.A"]], linetype="dotted", 
                color = "red", size=1)+
      scale_x_log10(
        breaks = scales::trans_breaks("log10", function(x) 10^x),
        labels = scales::trans_format("log10", scales::math_format(10^.x))
      ) +
      scale_y_log10(
        breaks = scales::trans_breaks("log10", function(x) 10^x),
        labels = scales::trans_format("log10", scales::math_format(10^.x))
      )+
      coord_cartesian(xlim = c(1e-2,1e3), ylim = c(1e-2,1e4))+
      theme_bw()+
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
      annotation_logticks()+
      xlab(x_label) + ylab(y_label)
    
  }
  
}

for(i in 1:length(gp)){
  gp[[i]]%>%plot()
}

```

#### Table Out

```{r message=FALSE, warning=FALSE, fig.show='hide', echo=FALSE, results='hide'}
#====|Generating HTML report|====####
list.of.packages <- c("htmltools","htmlTable","magrittr","xml2","dplyr","plotly","hwriter")
#Packages that does not install yet
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[, "Package"])]
#install required packages
if(length(new.packages)) {install.packages(new.packages)}
if(!require(spMisc)){remotes::install_github("GegznaV/spMisc")}
#Loading all packages
invisible(lapply(c(list.of.packages,list.of.packages), library, character.only = TRUE))
temp<-as.data.frame(gs_pop_get_count_fast(gs))
temp0<-as.data.frame(pData(gs))
temp0[temp$name,"well"]
temp<-cbind(
  Label=temp0[temp$name,"well"],
  temp
)
tableID<-"CountFast"
colnm<-colnames(temp)
TableResHTML.head<-hmakeTag('th',colnm,
                            style="font-weight: 900; border-bottom: 1px solid grey; border-top: 2px solid grey; text-align: center;"
)%>%
  paste(.,collapse="")%>%
  hmakeTag('tr',.)%>%hmakeTag('thead',.)

TableResHTML.body<-temp%>%
  hwrite(.,row.names=FALSE,col.names=FALSE,br=TRUE)%>%
  HTML()%>%read_html()%>%
  xml_find_all(.,".//tr")%>%as.character()%>%paste(.,collapse="")%>%
  hmakeTag('tbody',.)

TableResHTML<-hmakeTag('table',paste0(TableResHTML.head,TableResHTML.body))%>%
  HTML()%>%read_html()%>%xml_find_all(.,".//table")

xml_set_attrs(TableResHTML[[1]], c("id"=tableID, "cellpadding"="0"))
JS_HTML_src<-hmakeTag('script', src='./tablefilter/tablefilter.js')
JS_HTML<-hmakeTag(
  'script', id='data-config',
  data = paste0(
    "
    var filtersConfig = {
        base_path: 'tablefilter/',
        paging: {
         results_per_page: ['Records: ', [10, 25, 50, 100]]
       },
        col_0: 'select',
        col_1: 'select',
        col_2: 'select',
        col_3: 'select',
        popup_filters: true,
        alternate_rows: true,
        rows_counter: true,
        btn_reset: true,
        loader: true,
        status_bar: true,
        mark_active_columns: true,
        highlight_keywords: true,
        col_types: [
            'string', 'string', 'string',
            'string', 'number', 'number'
        ],
        custom_options: {
            cols:[4],
            sorts: [false]
        },
        extensions:[{
          name: 'sort'
        }]
    };

    var tf = new TableFilter('CountFast', filtersConfig);
    tf.init();
    "
  )
)
Body_HTML<-hmakeTag('body',paste0(TableResHTML,JS_HTML_src,JS_HTML))%>%
  HTML()%>%read_html()%>%xml_find_all(.,".//body")

as.character(Body_HTML)%>%HTML()
```

Below is the gating hierarchy structure

```{r fig.width=12, fig.height=7, results='hide', message=FALSE, warning=FALSE, fig.show='asis', echo=FALSE}
plot(gs, bool=TRUE)
```

## 03 Statics

### 03-01 Correlation Analysis {.tabset .tabset-fade}

#### Plot Out

```{r fig.width=9, fig.height=6, results='hide', message=FALSE, warning=FALSE, fig.show='asis', echo=FALSE}
library(gridExtra)
library(ggpubr)
library(plotrix)

LsOrder<-c(1:8,9:16,17:21)
gp <- list()
y1=c(150,150,150,50,175,150,150,150,150,150,150,150,150,150,150)
y2=c(125,125,125,25,150,125,125,125,125,125,125,125,125,125,125)
x0=c(7.5,125,125,300,50,200,50,200,200,100,3,50,50,200,200)
Label<-c()
CellP<-c()
Red_Mean<-c()
Red_SD<-c()
Red_SEM<-c()
PI_Mean<-c()
PI_SD<-c()
PI_SEM<-c()
Intercept<-c()
Slope<-c()
R2<-c()
PR<-c()
PP<-c()
SR<-c()
SP<-c()


for(i in 1:length(groups)){
  
  for(k in groups[[i]]){
    
    temp<-gh_pop_get_data(gs[[k]], paste0("No Debris"," (",groupNa[i],")", "/PI+ Red+"), returnType = "flowFrame")
    temp<-data.frame(
      "FL4.A"=temp@exprs[,"FL4.A"],
      "FL7.A"=temp@exprs[,"FL7.A"]
    )
    
    percentage<-gh_pop_get_data(gs[[k]], paste0("No Debris"," (",groupNa[i],")"), returnType = "flowFrame")
    percentage<-round(nrow(temp)/nrow(percentage)*100,3)
    
    
    if(nrow(temp)>2){
      lm.out<-lm(FL7.A~FL4.A, temp)
      pearson.out<-cor.test(temp$FL7.A, temp$FL4.A, method="pearson")
      spearman.out<-cor.test(temp$FL7.A, temp$FL4.A, method="spearman")
      
      #str(summary(lm.out))
      #str(summary(pearson.out))
      #str(summary(spearman.out))
      Intercept<-c(
        Intercept,
        summary(lm.out)$coefficients[1,1] # Intercept
      )
      Slope<-c(
        Slope,
        summary(lm.out)$coefficients[2,1] # Slope
      )
      R2<-c(
        R2,
        summary(lm.out)$r.squared # R^2
      )
      PR<-c(
        PR,
        pearson.out$estimate # pearson Rho
      )
      PP<-c(
        PP,
        pearson.out$p.value # pearson P-value
      )
      SR<-c(
        SR,
        spearman.out$estimate # spearman Rho
      )
      SP<-c(
        SP,
        spearman.out$p.value # spearman P-value
      )
    }else{
      Intercept<-c(
        Intercept,
        "NA" # Intercept
      )
      Slope<-c(
        Slope,
        "NA" # Slope
      )
      R2<-c(
        R2,
        "NA" # R^2
      )
      PR<-c(
        PR,
        "NA" # pearson Rho
      )
      PP<-c(
        PP,
        "NA" # pearson P-value
      )
      SR<-c(
        SR,
        "NA" # spearman Rho
      )
      SP<-c(
        SP,
        "NA" # spearman P-value
      )
    }
    
    Label<-c(
      Label,
      pData(gs)$well[k]
    )
    CellP<-c(
      CellP,
      percentage
    )
    Red_Mean<-c(
      Red_Mean,
      median(temp$FL7.A)
    )
    Red_SD<-c(
      Red_SD,
      sd(temp$FL7.A)
    )
    Red_SEM<-c(
      Red_SEM,
      std.error(temp$FL7.A)
    )
    PI_Mean<-c(
      PI_Mean,
      median(temp$FL4.A)
    )
    PI_SD<-c(
      PI_SD,
      sd(temp$FL4.A)
    )
    PI_SEM<-c(
      PI_SEM,
      std.error(temp$FL4.A)
    )
    
  }
  
}
```

#### Table Out

```{r message=FALSE, warning=FALSE, fig.show='hide', echo=FALSE, results='hide'}
library(openxlsx)

res.out<-data.frame(
  Label=Label,
  CellP=CellP,
  Red_Mean=Red_Mean,
  Red_SD=Red_SD,
  Red_SEM=Red_SEM,
  PI_Mean=PI_Mean,
  PI_SD=PI_SD,
  PI_SEM=PI_SEM,
  Intercept=Intercept,
  Slope=Slope,
  R2=R2,
  PR=PR,
  PP=PP,
  SR=SR,
  SP=SP
)

xlsx.res.out<-createWorkbook()

addWorksheet(xlsx.res.out, "FlowRes")
writeDataTable(xlsx.res.out, "FlowRes", res.out, startCol = 1, startRow = 1)

saveWorkbook(
  xlsx.res.out, 
  file = "00.Results.xlsx",
  overwrite = TRUE
)

temp<-res.out
tableID<-"ResOut"
colnm<-colnames(temp)
TableResHTML.head<-hmakeTag('th',colnm,
                            style="font-weight: 900; border-bottom: 1px solid grey; border-top: 2px solid grey; text-align: center;"
)%>%
  paste(.,collapse="")%>%
  hmakeTag('tr',.)%>%hmakeTag('thead',.)

TableResHTML.body<-temp%>%
  hwrite(.,row.names=FALSE,col.names=FALSE,br=TRUE)%>%
  HTML()%>%read_html()%>%
  xml_find_all(.,".//tr")%>%as.character()%>%paste(.,collapse="")%>%
  hmakeTag('tbody',.)

TableResHTML<-hmakeTag('table',paste0(TableResHTML.head,TableResHTML.body))%>%
  HTML()%>%read_html()%>%xml_find_all(.,".//table")

xml_set_attrs(TableResHTML[[1]], c("id"=tableID, "cellpadding"="0"))
JS_HTML_src<-hmakeTag('script', src='./tablefilter/tablefilter.js')
JS_HTML<-hmakeTag(
  'script', id='data-config',
  data = paste0(
    "
    var filtersConfig = {
        base_path: 'tablefilter/',
        paging: {
         results_per_page: ['Records: ', [10, 25, 50, 100]]
       },
        popup_filters: true,
        alternate_rows: true,
        rows_counter: true,
        btn_reset: true,
        loader: true,
        status_bar: true,
        mark_active_columns: true,
        highlight_keywords: true,
        col_types: [
            'string', 'number', 'number', 'number', 'number',
            'number', 'number', 'number', 'number', 'number',
            'number', 'number', 'number', 'number', 'number'
        ],
        custom_options: {
            sorts: [true]
        },
        extensions:[{
          name: 'sort'
        }]
    };

    var tf = new TableFilter('ResOut', filtersConfig);
    tf.init();
    "
  )
)
Body_HTML<-hmakeTag('body',paste0(TableResHTML,JS_HTML_src,JS_HTML))%>%
  HTML()%>%read_html()%>%xml_find_all(.,".//body")

as.character(Body_HTML)%>%HTML()

```

**Note:**

  * **Label**: Experiment treatment;
  * **CellP**: Cell Percentage (%);
  * **Red_Mean**: Averaged area of Alexa 633 channel;
  * **Red_SD**: Standard deviation of Red_Mean;
  * **Red_SEM**: Standard error of Red_Mean;
  * **PI_Mean**: Averaged area of PE/PI channel;
  * **PI_SD**: Standard deviation of PI_Mean;
  * **PI_SEM**: Standard error of PI_Mean;
  * **Intercept**: The Intercept of the fitted line;
  * **Slope**: The Slope of the fitted line;
  * **R2**: The R square of the fitted line;
  * **PR**: Pearson's Rho;
  * **PP**: The P-value of Pearson's Rho;
  * **SR**: Spearman's Rho;
  * **SP**: The P-value of Spearman's Rho.

<script src="http://kit.fontawesome.com/46057cf47a.js" crossorigin="anonymous"></script>
<script src="./HTML_source/script.js"></script>